Life in the canopy: Community trait assessments reveal substantial functional diversity among fern epiphytes

### 2020-01-15 ms/SI.rmd
Submit SI as pdf, not docx

---
title: ""
bibliography: 
  - "references_si.bib"
  - "references_other.yaml"
fontsize: 12pt
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
nocite: | 
  @NMNS2008, @Copeland1932, @FloraNSW2019, @Brownsey1987, @Nayar1971, @Lloyd1980, @Zhang2008, @Bierhorst1967, @Martin2006, @Tigerschiold1989, @Tigerschiold1990, @Atkinson1975, @Palmer2003
---

@@

Article acceptance date:

@@

```{r fig-s2}
library(corrr)

@@

ggsave(plot = fig_s1, filename = here::here("results/Fig_S1.eps"), height = 8, width = 4, units = "in")
```

@@

```{r fig-s1}
loadd(cwsd_scatterplot, cache = canopy_cache)
ggsave(plot = cwsd_scatterplot, filename = here::here("results/Fig_S2.eps"), height = 6, width = 7, units = "in")
```

>>>>

---
title: ""
bibliography: 
  - "references_si.bib"
  - "references_other.yaml"
fontsize: 12pt
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
    includes:
      in_header: new-phytologist.sty
header-includes: 
  - \usepackage{float}
  - \makeatletter\renewcommand*{\fps@figure}{H}\makeatother # Fix position of figs
  - \makeatletter\renewcommand*{\fps@table}{H}\makeatother # Fix position of tables
nocite: | 
  @NMNS2008, @Copeland1932, @FloraNSW2019, @Brownsey1987, @Nayar1971, @Lloyd1980, @Zhang2008, @Bierhorst1967, @Martin2006, @Tigerschiold1989, @Tigerschiold1990, @Atkinson1975, @Palmer2003
---

@@

Article acceptance date: ADD_DATE_WHEN_ACCEPTED

@@

\clearpage

```{r Fig-S1, fig.height = 8, fig.width = 4, fig.cap = ""}

@@

fig_s1

# ggsave(plot = fig_s1, filename = here::here("results/Fig_S1.eps"), height = 8, width = 4, units = "in")
```

\clearpage

```{r Fig-S2, fig.height = 6, fig.width = 7, fig.cap = ""}
loadd(cwsd_scatterplot, cache = canopy_cache)

cwsd_scatterplot

# ggsave(plot = cwsd_scatterplot, filename = here::here("results/Fig_S2.eps"), height = 6, width = 7, units = "in")
```

@@

\clearpage
